DraftOne

### 2016-06-13 DraftOne.Rmd
Adding functions to assess model performance

```{r}
sim_data <- function(n, rr, lambda, x_type = "binary", trend = "constant",
                     start.date = "2000-01-01", ...){

        require(dplyr)

        if(trend=="constant"){
          if(x_type == "binary"){
            x <- binary_exposure(n=n, ...)
          }
          else if(x_type == "continuous"){
            x <- continuous_exposure(n=n, ...)
          }
          exp_base_y <- constant_baseline(n=n, lambda = lambda, start.date = start.date)
          df <- full_join(x, exp_base_y, by="date") %>% mutate(exp_y = 
                 exp(log(exp_base_y)+log(rr)*x))
          df$y <- sapply(df$exp_y, FUN = function(x) rpois(1,x))
        }

        else if(trend != "constant"){
          if(x_type == "binary"){
            x <- season_binexp(n = n, ...)
          }
          else if(x_type == "continuous"){
            x <- season_contexp(n = n, trend = trend, ...)
          }
          exp_base_y <- seasonal_baseline(n = n, lambda = lambda, start.date = start.date,
                                          trend = trend)
          df <- full_join(x, exp_base_y, by="date") %>% mutate(exp_y = 
                exp(log(exp_base_y)+log(rr)*x))
          df$y <- sapply(df$exp_y, FUN = function(x) rpois(1,x))
        }
  return(df)
}

```

@@

```{r}
# Fit a generalized linear model
spline_mod <- function(df, df_year = 7){
        require(splines)

        dgrs_free <- df_year * as.numeric(diff(df[c(1, nrow(df)), "date"])) / 365.4
        df$time <- scale(df$date, center = TRUE, scale = FALSE)
        mod <- glm(y ~ x + ns(time, round(dgrs_free)),
                   data = df,
                   family = quasipoisson(link = "log"))

        out_1 <- summary(mod)$coef[2, ]
        out_2 <- confint.default(mod)[2, ]
        out <- c(out_1, out_2)
        return(out)
}
```

@@

```{r}
# Fit a case-crossover model
casecross_mod <- function(df){
        df$stratum <- factor(format(df$date, "%Y.%m"))

        if (sum(df$x == 0 | df$x == 1) == length(df$x)){
                event.check <- as.matrix(table(df$stratum, df$x))
                informative.strata <- rownames(event.check)[apply(event.check,
                                                          1, prod) > 0]
                df <- subset(df, stratum %in% informative.strata)

                if(length(informative.strata) > 1){
                        mod <- glm(y ~ x + stratum,
                                   data = df,
                                   family = quasipoisson(link = "log"))
                } else {
                        mod <- glm(y ~ x,
                                   data = df,
                                   family = quasipoisson(link = "log"))
                        }
        } else {
                mod <- glm(y ~ x + stratum,
                                   data = df,
                                   family = quasipoisson(link = "log"))
        }

        out_1 <- summary(mod)$coef[2, ]
        out_2 <- confint.default(mod)[2, ]
        out <- c(out_1, out_2)
        return(out)
}
```

@@

```{r}
# Fit a cross-year model
# Fit a case-crossover model
crossyear_mod <- function(df){
        df$stratum <- factor(format(df$date, "%j"))
        df$year <- factor(format(df$date, "%Y"))

        if (sum(df$x == 0 | df$x == 1) == length(df$x)){
                event.check <- as.matrix(table(df$stratum, df$x))
                informative.strata <- rownames(event.check)[apply(event.check,
                                                          1, prod) > 0]
                df <- subset(df, stratum %in% informative.strata)

                if(length(informative.strata) > 1){
                        mod <- glm(y ~ x + stratum,
                                   data = df,
                                   family = quasipoisson(link = "log"))
                } else {
                        mod <- glm(y ~ x,
                                   data = df,
                                   family = quasipoisson(link = "log"))
                        }
        } else {
                mod <- glm(y ~ x + stratum,
                                   data = df,
                                   family = quasipoisson(link = "log"))
        }

        out_1 <- summary(mod)$coef[2, ]
        out_2 <- confint.default(mod)[2, ]
        out <- c(out_1, out_2)
        return(out)
}
```

@@

```{r}
rep_sims <- function(n_sims, model, n = 5 * 365, rr = 1.01, 
                     x_type = "continuous", mu = 10, sd = 2, lambda = 100){
        library(dplyr)
        out <- replicate(n_sims, eval(call(model, 
                                           sim_data(n = n, rr = rr, 
                                                    x_type = x_type,
                                                    mu = mu, sd = sd,
                                                    lambda = lambda))))
        out <- as.data.frame(t(out))
        names(out) <- c("est", "se", "t", "p", "lower_ci", "upper_ci")
        return(out)
}
```

@@

```{r}
# Measure mean of estimated coefficient
mean_beta <- function(df){
        beta_hat <- mean(df$est)
        rr_hat <- mean(exp(df$est))
        out <- data.frame(beta_hat, rr_hat)
        return(out)
}
mean_beta(rep_df)
```

@@

```{r}
# Measure standard deviation across estimated coefficient
beta_var <- function(df){
        var_across_betas <- var(df$est)
        mean_beta_var <- mean(df$se^2)
        out <- data.frame(var_across_betas, mean_beta_var)
        return(out)
}
beta_var(rep_df)
```

>>>>

```{r}
sim_data 
```

@@

```{r}
# Fit a generalized linear model
spline_mod 
```

@@

```{r}
# Fit a case-crossover model
casecross_mod 
```

@@

```{r}
# Fit a cross-year model
crossyear_mod 
```

@@

```{r}
rep_sims 
```

@@

```{r}
# Measure mean of estimated coefficient
mean_beta 
mean_beta(rep_df)
```

@@

```{r}
# Measure standard deviation across estimated coefficient
beta_var 
beta_var(rep_df)
```
